---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---
# 3 Data visualisation with R
## 3.1 Exploring time-series data

```{r}
library(tidyverse)
```

```{r}
library(dplyr)
```

```{r}
library(lubridate)
```

```{r}
library(nycflights13)
```


```{r}
flightsEdited = flights %>%
mutate(date = make_date(year, month, day))
```

```{r}
flightsEdited
```
```{r}
flightsEdited %>%
select (year , month , day , date ) %>%
head
```
```{r}
daily = flightsEdited %>%
group_by(date) %>%
summarise (n=n())
head(daily)
```


```{r}
ggplot(daily, aes(date, n)) + geom_line()
```

```{r}
updatedFlightsEdited = flightsEdited %>%
mutate(weekday = wday(date, label = TRUE)) %>%
mutate(month = month(date, label = TRUE))
head(updatedFlightsEdited )
```


### Select just the data for January and compute the daily number of flights. Use ggplot to plot the data.

```{r}
jan_flights = filter(updatedFlightsEdited, month=="Jan")
```


```{r}
daily_jan = jan_flights %>%
  group_by(date) %>%
  summarise(n=n())
head(daily_jan)
```
```{r}
ggplot(daily_jan, aes(date, n)) + geom_line()
```

### Group the data by weekday and month and visualise which days and months have the most flights going to/from NYC (the main airports to NYC are JFK and LGA).

```{r}
head(updatedFlightsEdited)
```

```{r}
grouped_data = updatedFlightsEdited %>%
  group_by(month, weekday, origin, dest)%>%
  summarise(n=n()) %>%
  filter(origin=="JFK" | origin=="LGA" | dest == "JFK" | dest=="LGA")
head(grouped_data)
```
```{r}
grouped_data
```

```{r}
grouped_date = grouped_data %>%
  group_by(month, weekday)%>%
  summarise(n=n())%>%
  mutate(date = make_date(month, weekday))
head(grouped_date)
```

```{r}
grouped_date
```
```{r}
ggplot(grouped_date, aes(date, n)) + geom_line() + labs(x = "month", y = "flights to/from NYC", 
              title = "Flights")
```


## 3.2 Creating a correlation matrix

```{r}
data("mtcars")
str(mtcars)
```
### Correlation

```{r}
mcor = cor(mtcars)
round(mcor, digits =2)
```


```{r}
library(corrplot)
corrplot(mcor)
```



```{r}
library("GGally")
```


```{r}
ggcorr(mcor)
```

### Using the cor.test() function, determine the actual correlation score between cyl and disp.

```{r}
cor.test(mtcars$cyl, mtcars$disp, method = "pearson")
```

## 3.3 Creating a heatmap

```{r}
nba = read.csv("http://datasets.flowingdata.com/ppg2008.csv", sep=",")
head(nba)
```

```{r}
row.names(nba) = nba$Name
head(nba)
```

```{r}
nba = nba[ ,2:20]
```

```{r}
nbaMatrix = data.matrix(nba )
```

```{r}
nbaMatrix
```
```{r}
heatmap(nbaMatrix, Rowv = NA, Colv =NA, col = heat.colors(256), scale = "column", margins = c(5, 10))
```


