---
title: "Assignment-2"
output:
  word_document: default
  pdf_document: default
---


```{r}
medals = data.frame(Country =c("NOR", "GER ", " CHN"),
                    Gold =c(16 ,12 ,9) ,
                    Silver =c(8 ,10 ,4) ,
                    Bronze =c(13 ,5 ,2))
medals
```

### 1. Select the first and third rows and the first and third columns

```{r}
medals[c(1,3),c(1,4)]
```

### 2. Return a data frame that contains just the CHN row.

```{r}
medals[c(3),]
```
### 3. Return a data frame that contains the medals of Norway and Germany.

```{r}
medals[1:2,]
```

### 4. Select countries who won ten or more gold medals and return the Country and Gold columns using the subset() command.

```{r}
subset(medals, Gold > 10, select = c(Country, Gold))
```
### 5. Sort the medals by bronze (descending).

```{r}
medals[order(-medals$Bronze), ]
```

# Beijing2022 Olympic Games data


```{r}
beijing2022Medals = read.csv("Beijing2022.csv", header = FALSE, sep = ";")
colnames(beijing2022Medals) = c('Country','Gold','Silver','Bronze')
beijing2022Medals
```

```{r}
beijing2022Medals = beijing2022Medals[-1,]

```


```{r}
beijing2022Medals
```
### 1. Similar to what we did before try and compute the total number of medals won for each country and add this as a fifth column to beijing2022Medals.

```{r}
beijing2022Medals$Total_medals = beijing2022Medals$Gold + beijing2022Medals$Silver + beijing2022Medals$Bronze
beijing2022Medals
```

# 2. Order the rows by the total number of medals won.

```{r}
beijing2022Medals[order(-beijing2022Medals$Total_medals), ]
```

# 3. Sort the data first by the number of total medals won (in descending order) and then by the number of gold medals won (also in descending order).

```{r}
beijing2022Medals[order(-beijing2022Medals$Total_medals, -beijing2022Medals$Gold), ]
```

# 4. Calculate the total number of gold, silver and bronze medals won at Beijing 2022.

```{r}
Total_Gold = sum(beijing2022Medals[, c(2)])
Total_Gold
```
```{r}
Total_Silver = sum(beijing2022Medals[, c(3)])
Total_Silver
```
```{r}
Total_Bronze = sum(beijing2022Medals[, c(4)])
Total_Bronze
```


# 5. Work out the overall number of medals won by all countries in the Olympic Games in 2022?

```{r}
sum(beijing2022Medals["Total_medals"])
```

