---
output:
  word_document: default
  html_document: default
  pdf_document: default
---


# 3.1 Vectors

1. Create the following vector x = (1.2 2.3 0.2 1.1)

```{r}
x = c(1.2, 2.3, 0.2, 1.1)
print(x)
```
2. Check the class of the vector using the class() function.

```{r}
print(class(x))
```
3. Output the second element of the vector.


```{r}
print(x[2])
```
4. Output the elements 2 and 3 of the vector.

```{r}
print(x[2:3])
```
5. Replace the value of the first element of the vector.

```{r}
x[1]=0
print(x)
```

6. Select all elements where the value is greater than 2.

```{r}
x[x>2]
```
7. One very helpful feature of vectors is that if we apply functions they will typically
be carried out on all of the vectors. Square each value of x and assign it to a new
variable called x.squared().

```{r}
y = x**2
print(y)
```
8. Append the value 5.2 to x.

```{r}
x = append(x, 5.2)
print(x)
```
9. Compute the mean value of the updated vector x and check its length.

```{r}
mean_x = mean(x)
print(mean_x)
```
```{r}
print(length(x))
```
10. Create a named vector containing the number of days of each month. Further,
calculate the number of days in a year.

```{r}
days_months = c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
names(days_months) = c("jan", "feb", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")
print(days_months)
sum(days_months)
```

# 3.2 Vectors



```{r}
P = matrix( 
   c(2,3,4,5,6,7,8,9,1), # the data elements 
   nrow=3,              # number of rows 
   ncol=3,              # number of columns 
   byrow = TRUE)        # fill matrix by rows 
 
P                      # print the matrix 
```
1. Sum the values in the first row.

```{r}
sum(P[c(1,3),c(1,2)])
```
2. Sum the values in the first column.

```{r}
P[1,3]
```
3. Specifiy names for rows (“Row1, Row”) and columns (“Col1”, “Col2”).

```{r}
dimnames(P) = list( 
   c("row1", "row2","row3"),         # row names 
   c("col1", "col2", "col3")) # column names 
 
P                 # print A 
```

4. Select the second row in the matrix p using its name (“Row2”).

```{r}
P[c("row1", "row3"),c("col1","col2")]
```
5. Remove the third column from matrix p.

```{r}
P[-3,]

```
6. Add the column back again.

```{r}
P
```
7. Create a matrix to represent the medal table for the 2022 Beijing Winter Olympics
shown here: https://olympics.com/en/olympic-games/beijing-2022/medals. If
you just want to use the first few countries that’s fine. Assign names to the (Country)
rows and medal type (columns).

```{r}
MedalTable_beijinig_2022 = matrix( 
   c(1,2,1,7,7, 4,0,2,0,1,0,1,4,8,14,1,0,1), # the data elements 
   nrow=6,              # number of rows 
   ncol=3,              # number of columns 
   byrow = TRUE)        # fill matrix by rows 
 
dimnames(MedalTable_beijinig_2022) = list( 
   c("Australia", "Austria", "Belarus", "Belgium", "Canada", "Czech Republic"),         # row names 
   c("Gold", "Silver", "Bronze")) # column names 
 
MedalTable_beijinig_2022                 # print A 
```


# 3.3 Lists


```{r}
a = list ("a", 1, c(4 ,5 ,6))
print(a)
```
1. Return the elements 1 and 3 as a list.


```{r}
a[c(1,3)]
```
2. Provide each element position a name (e.g., “One”, “Two”, “Three”).

```{r}
names(a) = c("One", "Two", "Three")
```

```{r}
a
```

3. Select the first and third element using their name.

```{r}
a["One"]
```
```{r}
a["Three"]
```


