---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---

# 4 Multiple Linear Regression using R



```{r}
library(tidyverse)
```

```{r}
library(MASS)
```


```{r}
data("mtcars")
```

```{r}
? mtcars
```

```{r}
View(mtcars)
```


### model using only weight as variable

```{r}
mpgModel_wt = lm(formula = mpg ~ wt, data = mtcars)
```


```{r}
plot(mpgModel_wt, which =1)
```

```{r}
# Creating a data frame with actual values and predicted values.
mpgPredictions_wt = data.frame(mpg = mtcars$mpg, pred = mpgModel_wt$fitted.values)  
```

```{r}
mpgPredictions_wt
```
```{r}
ggplot(data = mpgPredictions_wt, aes(x = mpg , y = pred)) + geom_point() + geom_abline(mapping = aes(slope = 1, intercept = 0), color ='red ')
```

```{r}
summary(mpgModel_wt)
```
Residual standard error of the model with only weight as variable: 3.046

### model using all variable

```{r}
mpgModel_all = lm(formula = mpg ~ cyl + disp + hp + drat + wt + qsec + vs + am + gear + carb, data = mtcars)
```

```{r}
plot(mpgModel_all, which =1)
```

```{r}
# Creating a data frame with actual values and predicted values.
mpgPredictions_all = data.frame(mpg = mtcars$mpg, pred = mpgModel_all$fitted.values)  
```


```{r}
mpgPredictions_all
```
```{r}
ggplot(data = mpgPredictions_all, aes(x = mpg , y = pred)) + geom_point() + geom_abline(mapping = aes(slope = 1, intercept = 0), color ='red ')
```
```{r}
summary(mpgModel_all)
```
Residual standard error by using all variables in the model is: 2.65


### using the built in R step() function with backward option.

```{r}
reducedModel  = step(mpgModel_all, direction ="backward")
```
```{r}
summary(reducedModel)
```
Residual standard error by using step() function is: 2.459


```{r}
# Creating a data frame with actual values and predicted values.
mpgPredictions = data.frame(mpg = mtcars$mpg, pred_ConsideringOnlyWeight = mpgModel_wt$fitted.values, pred_ConsideringAll = mpgModel_all$fitted.values, pred_UsingStepFun = reducedModel$fitted.values)  
```


```{r}
mpgPredictions
```
As a summary:
1) Residual standard error of the model with only weight as variable: 3.046
2) Residual standard error by using all variables in the model is: 2.65
3) Residual standard error by using step() function is: 2.459

Hence by comparing Residual standard error, reducedModel by step function is a better fit for the data set.
Residual standard error of the other models with the subsets will be greater than 2.459
